---
title: "Peekbank Missingness and Zoning Exploration"
author: "Martin"
date: "5/2/2021"
output: html_document
---

```{r, message=FALSE}
library(peekbankr)
library(tidyverse)
library(lme4)
library(lmerTest)
library(tictoc)
library(langcog)
library(here)
library(DT)

figure_path <- here("vignettes","figures")

FIRST_TIME = FALSE # set to true first time to download data from DB

knitr::opts_chunk$set(cache = TRUE, warn = FALSE,warning=FALSE, message = FALSE,cache.lazy = FALSE)
```

## Get data

```{r, eval = FIRST_TIME}
con <- connect_to_peekbank()
datasets <- get_datasets(connection = con) %>% collect()
administrations <- get_administrations(connection = con) %>% collect()
subjects <- get_subjects(connection = con) %>% collect()
tic()
aoi_timepoints <- get_aoi_timepoints(connection = con) %>% collect()
toc()
stimuli <- get_stimuli(connection = con) %>% collect()
trial_types <- get_trial_types(connection = con) %>% collect()
trials <- get_trials(connection = con)  %>% collect()

dataset_info <- administrations %>%
  right_join(datasets) %>%
  right_join(subjects) 

aoi_data_joined <- aoi_timepoints %>%
  right_join(administrations) %>%
  right_join(trials) %>%
  right_join(trial_types) %>%
  right_join(datasets) %>%
  mutate(stimulus_id = target_id) %>%
  right_join(stimuli) %>%
  filter(t_norm > t_range[1],
         t_norm < t_range[2])

save(file = here("brm/data/aoi_data_joined.Rds"), aoi_data_joined)
save(file = here("brm/data/dataset_info.Rds"), dataset_info)
```

## Load data

```{r}
load(file = here("vignettes", "data","aoi_data_joined.Rds"))
dataset_name_mapping <- read_csv(here("vignettes","data","dataset_name_mapping.csv"))
aoi_data_joined <- aoi_data_joined %>%
  left_join(dataset_name_mapping)
```

## Compute missingness on trial level

We're summarizing missingness information on the trial level here for two windows:
1. the entire trial window
2. a crtical test window (here, a traditional 300-2000ms window - could be varied)

```{r}
#overall trial missingness and stickiness patterns
trial_missingness <- aoi_data_joined %>% group_by(dataset_name,dataset_rename,administration_id, subject_id,age, trial_id,trial_type_id) %>%
  summarize(
    num_obs=n(),
    window_size=max(t_norm)-min(t_norm),
    accuracy=case_when(
      sum(aoi %in% c("target","distractor"))==0 ~ NA_real_,
      TRUE ~ sum(aoi=="target")/(sum(aoi %in% c("target","distractor")))),
    percent_missing=sum(aoi %in% c("missing","other"))/num_obs,
    total_looking=sum(aoi %in% c("target","distractor")),
    percent_looking=total_looking/num_obs,
    zoner_trial=ifelse(accuracy ==0 | accuracy==1,1,0),
    zoner_type=case_when(
      accuracy==1 ~ "target",
      accuracy==0 ~ "distracter",
      TRUE ~ "none"
    )
  )


window_start <- 300
window_end <- 2000

#mean accuracy per trial
trial_accuracy <- aoi_data_joined %>% group_by(dataset_name,dataset_rename,administration_id, subject_id,age, trial_id,trial_type_id) %>%
  filter(t_norm>=window_start & t_norm <=window_end) %>%
  summarize(
    num_obs=n(),
    accuracy=case_when(
      sum(aoi %in% c("target","distractor"))==0 ~ NA_real_,
      TRUE ~ sum(aoi=="target")/(sum(aoi %in% c("target","distractor")))),
    percent_missing=sum(aoi %in% c("missing","other"))/num_obs,
    total_looking=sum(aoi %in% c("target","distractor")),
    percent_looking=total_looking/num_obs,
    zoner_trial=ifelse(accuracy ==0 | accuracy==1,1,0),
    zoner_type=case_when(
      accuracy==1 ~ "target",
      accuracy==0 ~ "distracter",
      TRUE ~ "none"
    )
  )


```

## What percentage of trials are missing & zoners, across dataset?

Percent zoners (either looking exclusively at target or distractor throughout entire trial).

```{r}

trial_missingness %>%
  group_by(dataset_rename) %>%
  summarize(
    percent_zoner_trials=mean(zoner_trial,na.rm=TRUE),
    percent_target_zoner=mean(accuracy==1,na.rm=TRUE),
    percent_distracter_zoner=mean(accuracy==0,na.rm=TRUE)) %>%
  DT::datatable()
  
```

Distribution of percent missing within the critical test window.

```{r}
trial_accuracy %>%
  filter(dataset_rename!="yoursmy") %>% #ignore yoursmy until it is updated
  ggplot(aes(x=percent_missing)) +
  geom_density() +
  facet_wrap(~dataset_rename,nrow=3)
```


## Relationship between percent missing and zoners to age

Upshot: Percent missing and zoning across the entire trial tends to decrease across age.

Percent missing across age

```{r}
#Percent missing
trial_accuracy %>%
  ggplot(aes(x=age,y=percent_missing)) +
  geom_point(alpha=0.2)+
  geom_smooth(method="lm")+
  facet_wrap(~dataset_rename,nrow=3)

m <- lmer(percent_missing ~ age + (1|subject_id)+(1|dataset_rename)+(1|trial_type_id),data=trial_accuracy)
summary(m)
```
Nice example that it's important to account for data set non-independence. If we ignore it, it looks like percent missing actually *increases* with age.

```{r}
trial_accuracy %>%
  ggplot(aes(x=age,y=percent_missing)) +
  geom_point(alpha=0.2)+
  geom_smooth(method="lm")

```

Distribution of zoners across age - "zoning" tends to decrease with age

```{r}
trial_missingness %>%
  ggplot(aes(x=age,y=zoner_trial)) +
  geom_point(alpha=0.2)+
  geom_smooth(method="lm")+
  facet_wrap(~dataset_rename,nrow=3)

#zoners
m <- glmer(zoner_trial ~ age + (1|subject_id)+(1|dataset_rename)+(1|trial_type_id),data=trial_accuracy,family=binomial)
summary(m)
```

## Relationship between "Zoning" (subjects) and accuracy

It appears that having a higher percentage of zoning trials in general is related to slightly lower accuracy

```{r}
#compute percent zoner trials for each participant
subj_zoners <- trial_missingness %>%
  group_by(dataset_name,dataset_rename, subject_id) %>%
  summarize(
    num_trials=n(),
    num_zoner_trials=sum(zoner_trial,na.rm=TRUE),
    percent_zoner_trials=num_zoner_trials/num_trials
  )
#compute accuracy for a 300-2000 target window
subj_accuracy <- trial_accuracy %>%
  group_by(dataset_name,dataset_rename,subject_id) %>%
  mutate(
    weighted_age=mean(age,na.rm=TRUE)
  ) %>%
  group_by(dataset_name,dataset_rename,subject_id,weighted_age) %>%
  summarize(
    num_trials=n(),
    mean_accuracy=mean(accuracy,na.rm=TRUE)
  )  

#combine
subj_accuracy <- subj_accuracy %>%
  left_join(subj_zoners, by=c("dataset_rename","subject_id"))

#Plot relationship between percent zoner trials and accuracy
ggplot(subj_accuracy,aes(percent_zoner_trials, mean_accuracy,color=dataset_rename))+
  geom_point(alpha=0.2)+
  geom_smooth(method="lm",se=FALSE)
```


Number of trials and relation to reliability?

TO DO

