---
title: "Peekbank Descriptives"
author: "peekbank team"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---


```{r, message=F, warning=F}
library(knitr)
library(peekbankr)
library(tidyverse)
library(lme4)
library(lmerTest)
library(tictoc)
library(langcog)
library(here)
library(cowplot)
library(formattable)
theme_set(theme_cowplot())
#library(tidymodels)

figure_path <- here("figures")

load(file = "data/aoi_data_joined.Rds")
knitr::opts_chunk$set(cache = FALSE, warning = FALSE, message = FALSE,cache.lazy = FALSE)
dataset_name_mapping <- read_csv(here("data","dataset_name_mapping.csv"))

con <- connect_to_peekbank()
stimuli <- get_stimuli(connection = con) %>% collect()
subjects <- get_subjects(connection = con) %>% collect()

aoi_data_joined <- aoi_data_joined %>%
  left_join(subjects)


```

The goal is to report general statistics for the CogSci paper.

## Preparing the data 

### Fit and filter trial accuracy (proportion looking to target)

Compute trial-level accuracy (proportion looking to the target) in a fixed critical window (300-2000ms).

```{r}
t_min <- 300
t_max <- 2000

by_trial_means <- aoi_data_joined %>%
  #window of analysis
  filter(t_norm > t_min, t_norm < t_max) %>%
  mutate(age_binned = cut(age, seq(12,60,12))) %>%
  rename(target_label = english_stimulus_label) %>%
  group_by(subject_id, trial_id, stimulus_novelty,target_label, distractor_id,
           age, age_binned) %>%
  summarise(prop_looking = sum(aoi == "target", na.rm = TRUE) / 
              (sum(aoi == "target", na.rm=TRUE) + 
                 sum(aoi=="distractor", na.rm=TRUE)),
            prop_missing = mean(aoi == "missing", na.rm = TRUE)) %>%
  left_join(stimuli %>% select(-stimulus_novelty), by = c("distractor_id" = "stimulus_id")) %>%
  rename(distractor_label = english_stimulus_label)

unique_stimuli <- by_trial_means %>%
  ungroup() %>%
  select(dataset_name,target_label) %>%
  distinct() %>%
  group_by(dataset_name) %>%
  summarize(
    unique_items=n()
  )
  
```

Filter the data to trials where there is sufficient looking data (target or distractor looking on at least 2/3 of the trial)

```{r}
by_trial_means <- by_trial_means %>%
  ungroup() %>%
  filter(prop_missing < 1/3) %>%
  mutate(age_centered = age - mean(age,na.rm=TRUE))

```

## Summarize proportion looking by participant by dataset

```{r}
by_participant_means <- by_trial_means %>%
  ungroup() %>%
  group_by(dataset_name,subject_id) %>%
  summarize(
    trial_n=n(),
    unique_items=length(unique(target_label)),
    avg_prop_looking=mean(prop_looking,na.rm=TRUE),
    # avg_prop_looking_ci=qt(0.975, trial_n-1)*sd(prop_looking,na.rm=TRUE)/sqrt(trial_n),
    # avg_prop_looking_lower_ci=avg_prop_looking-avg_prop_looking_ci,
    # avg_prop_looking_upper_ci=avg_prop_looking+avg_prop_looking_ci,
    age=mean(age,na.rm=TRUE)
  ) 

write_csv(by_participant_means,here("data","participant_means_prop_looking.csv"))
```

### Plot accuracy against age

```{r}
ggplot(by_participant_means,aes(age,avg_prop_looking))+
  geom_point(aes(size=trial_n))+
  geom_smooth(method="lm")+
  xlab("Age (in months)")+
  ylab("Proportion Target Looking")+
  geom_hline(yintercept=0.5, linetype="dashed",size=1.2)
```


### Predict accuracy from age

#### Across trials

```{r}
m <- lmer(prop_looking ~ age+(1|subject_id)+(1|dataset_name),data=by_trial_means)
summary(m)
```


#### Participant averages

```{r}
m <- lmer(avg_prop_looking ~ age+(1|dataset_name),data=by_participant_means)
summary(m)
```


## Summarize proportion looking by dataset

```{r}
dataset_means <- by_participant_means %>%
  ungroup() %>%
  group_by(dataset_name) %>%
  summarize(
    N=n(),
    mean_age=round(mean(age,na.rm=TRUE),0),
    min_age=round(min(age,na.rm=TRUE),0),
    max_age=round(max(age,na.rm=TRUE),0),
    prop_looking=mean(avg_prop_looking,na.rm=TRUE),
    prop_looking_ci=qt(0.975, N-1)*sd(avg_prop_looking,na.rm=TRUE)/sqrt(N),
    prop_looking_lower_ci=prop_looking-prop_looking_ci,
    prop_looking_upper_ci=prop_looking+prop_looking_ci,
  ) %>%
  select(-prop_looking_ci) %>%
  left_join(unique_stimuli) %>%
  relocate(unique_items,.after=N)

dataset_means %>%
  formattable()
write_csv(dataset_means,here("data","dataset_means_prop_looking.csv"))
```

## Summarize proportion looking by participant by dataset by stimulus novelty

```{r}
by_participant_means_novelty <- by_trial_means %>%
  ungroup() %>%
  group_by(dataset_name,subject_id,stimulus_novelty) %>%
  summarize(
    trial_n=n(),
    avg_prop_looking=mean(prop_looking,na.rm=TRUE),
    age=mean(age,na.rm=TRUE)
  )

write_csv(by_participant_means_novelty,here("data","participant_means_prop_looking_novelty.csv"))
```

## Summarize proportion looking by dataset by stimulus novelty
```{r}
dataset_means_novelty <- by_participant_means_novelty %>%
  ungroup() %>%
  group_by(dataset_name,stimulus_novelty) %>%
  summarize(
    N=n(),
    mean_age=round(mean(age,na.rm=TRUE),0),
    min_age=round(min(age,na.rm=TRUE),0),
    max_age=round(max(age,na.rm=TRUE),0),
    prop_looking=mean(avg_prop_looking,na.rm=TRUE),
    prop_looking_ci=qt(0.975, N-1)*sd(avg_prop_looking,na.rm=TRUE)/sqrt(N),
    prop_looking_lower_ci=prop_looking-prop_looking_ci,
    prop_looking_upper_ci=prop_looking+prop_looking_ci,
  ) %>%
  select(-prop_looking_ci)

dataset_means_novelty %>%
  formattable()
write_csv(dataset_means,here("data","dataset_means_prop_looking_novelty.csv"))
```

### Predict accuracy from stimulus novelty

#### Across trials

```{r}
m <- lmer(prop_looking ~ stimulus_novelty+(1|subject_id)+(1|dataset_name),data=by_trial_means)
summary(m)
```


#### Participant averages

```{r}
m <- lmer(avg_prop_looking ~ stimulus_novelty+(1|dataset_name),data=by_participant_means_novelty)
summary(m)
```